Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-11-07 docs/Truman/LocalConservation/paper/paper.tex

\def\btau{\boldsymbol\tau}
\def\bsigma{\boldsymbol\sigma}
\def\bbeta{\boldsymbol\beta}
\def\blambda{\boldsymbol\lambda}

@@

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\snorm}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}
\newcommand{\ptl}{{\partial}}
\newcommand{\bfsig}{\mbox{\boldmath $\sigma$}}
\newcommand{\bfn}{\mbox{\boldmath $n$}}
\newcommand{\bfH}{\mbox{\boldmath $H$}}
\newcommand{\HdivK}{\bfH(\text{div},K)}
\newcommand{\HOneK}{H^{1}(K)}
\newcommand{\HOneOmegah}{H^{-1}(\Omega_h)}
\newcommand{\HdivOmegah}{\bfH(\text{div},\Omega_h)}
\newcommand{\vdeltau}{v_{\delta\bs u_h}}
\newcommand{\taudeltau}{\btau_{\delta\bs u_h}}

@@

% We can decompose the discrete flux space $\hat F_h$ into equilibriated fluxes
% (zero net flux over each element) and some algebraic complement:
% \begin{equation}
% \hat F_h=\hat F_h^e\oplus\hat F_h^{ne}\,,\quad\hat
% F_h^{e}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
% \label{eq:decomposition}
% \end{equation}
% In theory, we could accomplish this by employing for fluxes in $\hat F_h^{e}$
% traces of curls, $\nabla\times\phi$, but we don't do this in practice.
%
% \textcolor{red}{
% In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully
% coupled system of equations, but for didactic purposes, we can examine it one
% piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$ to
% $\delta\hat t\in\hat F_h^{ne}$, the Lagrange multiplier term drops out and we
% are left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$,
% and $\hat t_h^e\in\hat F^e_h$.
% }
%
% \textcolor{red}{
% Restricting ourselves to $\delta\hat t\in\hat
% F_h^{e}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
% equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
% t\in\hat F_h^e$. The remaining fluxes, $\hat t\in\hat F_h^{ne}$ are determined
% from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
% t\in\hat F_h^{ne}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
% system of equations that can be solved for Lagrange multipliers $\lambda_K$.
% }
%
% \subsection{\textcolor{red}{Proof of Convergence}}
% In the following discussion, we do not account for the error in approximating
% the optimal test functions because $\dots$ (Need explanation).
% We cannot directly use Brezzi's theorem, but we can reproduce his argument.
% First of all, variational formulation \eqref{eq:variationalFormulation} is
% equivalent to:
%
% Find $\bs u\in\bs U$ such that
% \begin{equation}
% b(\bs u,T(\delta\bs u))=(f,T(\delta\bs u))\quad\forall\bs v\in\bs V\,.
% \label{eq:bilinearForm}
% \end{equation}
% This is because the trial-to-test operator $T=R_V^{-1}B$ is an isomorphism.
%
% Restricting ourselves to $\delta\hat t_h\in\hat F_h^e$, and subtracting
% \eqref{eq:bilinearForm} from \eqref{eq:conservativeConfusionSystem}, we have
% the Galerkin orthogonality condition:
% \begin{align}
% \label{eq:galerkinOrthogonality}
% \frac{1}{\epsilon}(\bsigma_h-\bsigma,\taudeltau)
% &+(u_h-u,\nabla\cdot\taudeltau)
% -\langle\hat u_h-\hat u,\taudeltau\cdot\bs n\rangle
% \nonumber\\
% &-(\bbeta(u_h-u)-(\bsigma_h-\bsigma),\nabla\vdeltau)
% +\langle\hat t_h-\hat t,\vdeltau\rangle
% \\
% &\hspace{25ex}\forall(\delta u_h,\delta\bsigma_h,\delta\hat u_h,\delta\hat t_h)
% \in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
% \nonumber
% \end{align}
%
% We begin with an equivalent of Brezzi's \emph{discrete inf-sup in kernel
% condition}.
% \begin{lemma}
% \label{lemma:infsuplemma}
% The following condition holds:
% \begin{align}
% \sup_{\stackrel{
% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
% }
% \frac{\snorm{
% b((u_h,\bsigma_h,\hat u_h,\hat t_h), (\vdeltau,\taudeltau))
% % \frac{1}{\epsilon}(\bsigma_h,\taudeltau)
% % +(u_h,\nabla \cdot\taudeltau)
% % -\langle\hat u_h,\taudeltau\cdot\bs n\rangle
% % -(\bbeta u_h-\bsigma_h,\nabla\vdeltau)
% % +\langle\hat t_h,\vdeltau\rangle
% }}
% {\norm{(\vdeltau,\taudeltau)}}
% \ge\alpha\norm{(u_h,\bsigma_h,\hat u_h,\hat t_h)}\quad\nonumber\\
% \forall(u_h,\bsigma_h,\hat u_h,\hat t_h)
% \in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
% \label{eq:infsup}
% \end{align}
%
% \end{lemma}
% \begin{proof}
% By the very construction of the trial-to-test operator, the supremum on the
% left is equal to
% \begin{equation}
% \norm{T(u_h,\bsigma_h,\hat u_h,\hat t_h)}_{V}
% =\norm{R_V^{-1}B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V}
% =\norm{B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V'}
% \label{eq:infsupproof}
% \end{equation}
% The condition follows now from the fact that operator $B$ is bounded below,
% i.e. bilinear form \linebreak$b((u_h,\bsigma_h,\hat u_h, \hat t_h),(v,\btau))$ satisfies
% the inf-sup condition.
% \end{proof}
%
% Assume additionally that flux decomposition \eqref{eq:decomposition} is
% orthogonal. We begin by decomposing $\hat t_h$,
% \begin{equation}
% \hat t_h=\hat t_h^{e}+\hat t_h^{ne}\,.
% \label{eq:fluxdecomposition}
% \end{equation}
% Next, we use the triangle inequality,
% \begin{align}
% \label{eq:triangle}
% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-\hat t_h)}&=
% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^e+\hat t_h^{ne}))}\nonumber\\
% &\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^e+\hat t_h^{ne}))}\\
% &\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\nonumber
% \end{align}
% where $w_h\in U_h$, $\bs s_h\in\bs S_h$, $\hat w_h\in\hat U_h$, and $\hat
% r_h^{e}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
% implies:
% \begin{align}
% \label{eq:estimate}
% &\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\\
% &\hspace{8ex}\le\frac{1}{\alpha}
% \sup_{\stackrel{
% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
% }
% \frac{\snorm{
% b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e-\hat t_h^e),
% (\vdeltau,\taudeltau))
% }}
% {\norm{(\vdeltau,\taudeltau)}}\nonumber\\
% &\hspace{8ex}\le\frac{1}{\alpha}
% \sup_{\stackrel{
% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
% }
% \frac{\snorm{
% b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e+\hat t_h^{ne}-\hat t),
% (\vdeltau,\taudeltau))
% }}
% {\norm{(\vdeltau,\taudeltau)}}\nonumber\\
% &\hspace{8ex}\le\frac{1}{\alpha}
% \norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^e+\hat
% t_h^{ne}))}
% \end{align}
% % \frac{1}{\epsilon}(\bs s_h-\bsigma_h,\taudeltau)
% % +(w_h-u_h,\nabla \cdot\taudeltau)
% % -\langle\hat w_h-\hat u_h,\taudeltau\cdot\bs n\rangle
% % -(\bbeta (w_h-u_h)-(\bs s_h-\bsigma_h),\nabla\vdeltau)
% % +\langle\hat r_h^e-\hat t_h^e,\vdeltau\rangle
% where the second step follows from the Galerkin orthogonality condition
% \eqref{eq:galerkinOrthogonality}, and the last step is a consequence of the
% minimum energy extension norm for fluxes. Combining with \eqref{eq:triangle},
% we get the final stability result:
% \begin{equation}
% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h,\hat t-\hat t_h)}
% \leq\left(1+\frac{1}{\alpha}\right)
% \inf_{\stackrel{
% (w_h,\bs s_h,\hat w,\hat r_h^e)\in}
% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
% }
% \norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^e+\hat t_h^{ne}))}
% \,.
% \label{eq:stability}
% \end{equation}

>>>>

\def\btau{\boldsymbol\tau}
\def\bftau{\boldsymbol\tau}
\def\bsigma{\boldsymbol\sigma}
\def\bbeta{\boldsymbol\beta}
\def\blambda{\boldsymbol\lambda}

@@

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\snorm}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}
\newcommand{\ptl}{{\partial}}
\newcommand{\bfsig}{\mbox{\boldmath $\sigma$}}
\newcommand{\bfv}{\boldsymbol v}
\newcommand{\bfu}{\boldsymbol u}
\newcommand{\bfpsi}{\boldsymbol\psi}
\newcommand{\bflambda}{\boldsymbol\lambda}
\newcommand{\bfn}{\mbox{\boldmath $n$}}
\newcommand{\bfH}{\mbox{\boldmath $H$}}
\newcommand{\HdivK}{\bfH(\text{div},K)}
\newcommand{\HOneK}{H^{1}(K)}
\newcommand{\HOneOmegah}{H^{-1}(\Omega_h)}
\newcommand{\HdivOmegah}{\bfH(\text{div},\Omega_h)}
\newcommand{\vdeltau}{v_{\delta\bs u_h}}
\newcommand{\taudeltau}{\btau_{\delta\bs u_h}}

@@

%%%%%%%%%%% Begin Demkowicz Section %%%%%%%%%%%%
\subsection{Stability Analysis}

In the following analysis, we neglect the error due to the approximation of optimal test functions.
We follow the classical Brezzi's theory \cite{Brezzi1974,DBB05} for an abstract
mixed problem:
\begin{equation}
\left\{
\begin{array}{lll}
u \in V, p \in Q\\
a(u,v) + c(p,v) & = l(v) & \forall v \in V \\
c(q,u) & = g(q) & \forall q \in Q
\end{array}
\right.
\end{equation}
where $V,Q$ are Hilbert spaces, and $a,c,l,q$ denote the appropriate
bilinear and linear forms.

The choice of norm for the Lagrange multipliers $\lambda_K$ is implied
by the quotient norm used for $H^{-1/2}(\Gamma_h)$ and continuity
bound for form $c(p,v)$ representing the constraint.
\begin{equation}
\begin{array}{lll}
\vert b((u,\bfsig,\hat{u},\hat{t}),\sum_K \lambda_K (1_K,{\bf 0})) \vert
& = \vert \sum_K \lambda_K \langle \hat{t}, 1_K \rangle_{\ptl K} \vert \\[8pt]
& = \vert \sum_K \lambda_K \langle v_n , 1_K \rangle_{\ptl K} \vert \\[8pt]
& = \vert \sum_K \lambda_K \int_K \text{div} \bfv \: 1_K  \vert \\[8pt]
& \leq \sum_K  \lambda_K \Vert \text{div} \bfv \Vert_{L^2(K)} \mu(K)^{1/2} \\[8pt]
& \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K \Vert \text{div} \bfv \Vert_{L^2(K)}^2 )^{1/2} \\[8pt]
& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: \Vert \bflambda \Vert} \Vert \hat{t} \Vert_{H^{-1/2}(\Gamma_h)}
\end{array}
\end{equation}
Above, function $\bfv$ denotes the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
that realizes the minimum in the definition of the quotient (minimum energy extension) norm,
and $\mu(K)$ stands for the area (measure) of element $K$.

We proceed now with the discussion of the discrete inf-sup stability constants. We skip
index $h$ in the notation.

\paragraph{Inf Sup Condition} relating spaces $V$ and $Q$ reads as follows,
\begin{equation}
\sup_{v \in V} \frac{\vert c(p,v) \vert}{\Vert v \Vert_V} \geq \beta \Vert p \Vert_Q
\end{equation}
Let
\begin{equation}
R\, : \, L^2(\Omega) \ni q \to \bfv \in \bfH(\text{div},\Omega) \cap \bfH^1(\Omega)
\end{equation}
be
the continuous right inverse of the divergence operator constructed by
Costabel and McIntosh in \cite{CostabelMcIntosh}.
Let $\bfv_h$ denote the classical, lowest order Raviart-Thomas (RT) interpolant of
function
\begin{equation}
\bfv = R (\sum_K \lambda_K 1_K) \: .
\end{equation}
Note that $\text{div} \bfv_h = \text{div} \bfv = \lambda_K$ in element $K$.

Classical $h$-interpolation interpolation error estimate for the lowest error
Raviart-Thomas elements and continuity of operator $R$ imply the stability estimate:
\begin{equation}
\begin{array}{lll}
\Vert \bfv_h \Vert & \leq \Vert \bfv_h - \bfv \Vert + \Vert \bfv \Vert\\[8pt]
&\leq C h \Vert \bfv \Vert_{H^1} +  \Vert \bfv \Vert \\[8pt]
& \leq C \Vert \text{div} \bfv \Vert = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
\end{array}
\label{eq:stab}
\end{equation}
Above, $C$ is a generic, mesh independent constant incorporating constant from
the interpolation error estimate and continuity constant of $R$.
Let $\hat{t}$ be now the trace of $\bfv_h$. We have then,
\begin{equation}
\sup_{\hat{t} \in H^{-1/2}(\Gamma_h)} \frac{\vert  \sum_K \lambda_K \langle \hat{t},1_K \rangle_{\ptl K} \vert}{\Vert \hat{t} \Vert_{H^{-1/2}(\Gamma_h)}}
\geq \frac{\vert \sum_K \lambda_K \int_K \text{div} \bfv_h \: 1_K  \vert}
{\Vert \bfv_h \Vert_{H(\text{div},\Omega)}}
\geq \frac{1}{C} (\sum_K \mu(K) \lambda_K^2)^{1/2}
\end{equation}
where $C$ is the constant from stability estimate~(\ref{eq:stab}).

Notice that we have considered traces of lowest order Raviart-Thomas elements for the
discretization of flux $\hat{t}$. The inf-sup condition for the lowest order RT spaces implies
automatically the analogous condition for elements of arbitrary order; increasing
space $V$ makes only the discrete inf-sup constant bigger.

\paragraph{Inf Sup in Kernel Condition} is satisfied automatically due to the use of optimal
test functions. First of all, we characterize the ``kernel'' space:
\begin{equation}
\begin{array}{rl}
V_0  := & \{ v \in V \, : \, c(v,u) = 0 \: \forall q \in Q\} \\[8pt]
 = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_T \rangle = 0 \, \forall K \}
\end{array}
\end{equation}
In other words, the kernel space contains only the equilibriated fluxes.
With $u \in V_0$, we have then:
\begin{equation}
\sup_{v \in V_0} \frac{\vert a(u,v) \vert}{\Vert v \Vert_V }
 \geq \frac{\vert b(\bfu,T \bfu) \vert}{\Vert T \bfu \Vert}
= \sup_{(v,\bftau)}
\frac{\vert b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) \vert}{\Vert (v,\bftau) \Vert}
\geq \gamma \Vert (u,\bfsig,\hat{u},\hat{t}) \Vert
\end{equation}
where $\gamma$ is the stability constant for the standard continuous DPG formulation.

With both discrete inf-sup constants in place, we have the standard result: the FE error
is bounded by the best approximation error. Notice that the exact Lagrange multipliers
are zero, so the best approximation error involves only solution $(u,\bfsig,\hat{u},\hat{t})$.

\subsubsection{Robustness Analysis}

Recall the main line of analysis in \cite{} leading to the construction of robust
test norms. With the robust test norms, we have
\begin{equation}
\begin{array}{ll}
\Vert u - u_h \Vert, \Vert \bfsig - \bfsig_h \Vert
& \lesssim \Vert (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h \Vert_E \\[8pt]
&= \inf_{(v_h,\bftau_h,\hat{v},\hat{r}_h)}
\Vert (u - v_h, \bfsig - \bftau_h, \hat{u} - \hat{v}_h, \hat{t} - \hat{r}_h \Vert_E
\end{array}
\end{equation}
The last equality follows from the fact that DPG method delivers the best approximation
error in the energy norm (minimizes the residual). This is not longer true for the
conservative version. So, can we claim the robustness in the sense of the inequality above
for the conservative version as well ?

One possible way to attack the problem is to switch to the energy norm in the Brezzi's stability
analysis. Dealing with the ``inf-sup in kernel'' condition is simple. Upon replacing
the original norm of solution $u$ with the energy norm, both constant $\gamma$ and continuity
constant become unity. In order to investigate the robustness of inf-sup  constant $\beta$,
we need to realize first what the energy norm of flux $\hat{t}$ is. Given an element $K$,
we solve for the optimal test functions corresponding to flux $\hat{t}$,
\begin{equation}
\left\{
\begin{array}{ll}
v_K \in H^1(K),\, \bftau_K \in \bfH(\text{div},K)\\[8pt]
((v_K,\bftau_K), (\delta v,\delta \bftau)_V = \langle \hat{t},\delta v\rangle_{\ptl K}
\quad \forall \delta v \in H^1(K), \delta \bftau \in \bfH(\text{div},K)
\end{array}
\right.
\label{eq:local_problem}
\end{equation}
The energy norm of $\hat{t}$ is then equal to:
\begin{equation}
\Vert \hat{t} \Vert_E^2 = \sum_K \Vert (v_K,\bftau_K) \Vert_V^2
\end{equation}
We need to establish sufficient conditions under which inf-sup and continuity constants for
the bilinear form representing the constraint are independent of viscosity $\epsilon$.

Let us start with the inf-sup condition,
\begin{equation}
\sup_{\hat{t}} \frac{\vert \sum_K \lambda_K \langle \hat{t},1_K \rangle \vert}{\Vert \hat{t} \Vert_E}
\geq  \beta (\sum_K \mu(K) \lambda_K^2)^{1/2}
\end{equation}
As in the previous analysis, we select for $\hat{t}$ the trace of Raviart-Thomas
interpolant $\bfpsi_h$ of $\bfpsi = R (\sum_K \lambda_K 1_K)$ where $R$ is the right-inverse
of the divergence operator constructed by Costabel and Mac Intosh. The only change compared
with the previous analysis, is the evaluation of norm of $\hat{t}_h$. For this, we need
to solve the local problems:
\begin{equation}
((v,\bftau), (\delta v, \delta \bftau)_V = \langle \hat{t}, \delta v \rangle_{\ptl K}
= \int_K \text{div} \bfpsi_h \, \delta v = \int_K \text{div} \bfpsi \, \delta v = \int_K \lambda_K \delta v
= \lambda_K (1_K,\delta v)_K  \quad \forall \delta v \in H^1(K)
\label{eq:local}
\end{equation}
We need then an upper bound of the energy norm of $\bfv_h$:
$$
(\sum_K \Vert (v,\bftau) \Vert_V^2)^{1/2}
$$
Substituting $v$ for $\delta v$ in~(\ref{eq:local}), we get,
\begin{equation}
\Vert (v,\bftau) \Vert_V^2 = \lambda_K (1_K, v_K)
\end{equation}
If we have a robust stability estimate:
\begin{equation}
(1_K, v_K) \leq C \mu(K)^{1/2} \Vert (v,\bftau) \Vert_K
\end{equation}
(i.e. constant $C$ is independent of $\epsilon$) then
\begin{equation}
\Vert  (v,\bftau) \Vert_V \leq C \mu(K)^{1/2} \vert \lambda_K \vert
\end{equation}
and, eventually, as needed,
\begin{equation}
\sum_K \Vert (v,\bftau) \Vert_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
\end{equation}
which leads to the robust estimate of inf-sup constant $\beta$. For example, it is sufficient if
\begin{equation}
\Vert v \Vert_{L^2(K)} \leq \Vert v \Vert_V \, .
\label{eq:robust_est1}
\end{equation}
Notice that the stability analysis with the energy norm was, in a sense, easier than
with the quotient norm. Only the divergence of the interpolant $\bfpsi_h$ enters~(\ref{eq:local})
and it coincides with the divergence of $\bfpsi$.

We arrive at a similar situation in the continuity estimate of
$$
\sum_K \lambda_K \langle \hat{t}, 1_K \rangle
$$
Testing with $(1_K,{\bf 0})$ in the local problem~(\ref{eq:local_problem}), we obtain,
\begin{equation}
((v,\bftau),(1_K,{\bf 0}))_V = \langle \hat{t}, 1_K \rangle_{\ptl K}
\label{eq:local2}
\end{equation}
If we have a robust estimate,
\begin{equation}
\vert ((v,\bftau),(1_K,{\bf 0}))_V \vert \leq C \mu(K)^{1/2} \, \Vert (v,\bftau) \Vert_V
\label{eq:robust_est2}
\end{equation}
then
\begin{equation}
\vert \sum_K \lambda_K \langle \hat{t}, 1_K \rangle \vert \leq C (\sum_K \mu(K) \lambda_K^2)^{1/2}
\, (\sum_K \Vert (v,\bftau) \Vert_V^2)^{1/2}
= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  \Vert \hat{t} \Vert_E
\end{equation}
as needed.

For instance, condition~(\ref{eq:robust_est2}) will be satisfied if the test inner product
in~(\ref{eq:local2}) reduces to the $L^2$ term only,
\begin{equation}
((v,\bftau),(1_K,{\bf 0}))_V = (v,1_K)_{L^2(K)} \: .
\end{equation}
With the robust stability and continuity constants for the mixed problem, the energy error
of solution $(u,\bfsig,\hat{u},\hat{t})$ (and Lagrange multipliers $\lambda_K$ as well)
is bounded robustly by the {\em best approximation error} of  $(u,\bfsig,\hat{u},\hat{t})$
measured in the energy norm. We arrive thus at the same situation as in the standard
DPG method.

% %%%%%%%%%%% End Demkowicz Section %%%%%%%%%%%%
